MS_CNuptake.Rmd

### 2022-10-14 MS_CNuptake.Rmd
update metric_info

larger_size <- theme(axis.text=element_text(size=20),axis.title=element_text(size=20),
                     plot.subtitle=element_text(size=15))
```

@@

@@

#check some percentage
dim(subset(NPP_all, is.na(Nmin)==T & pft =="Forest"))
dim(subset(NPP_all, is.na(Nmin)==T & pft =="Grassland"))

dim(subset(NPP_all, is.na(Nmin)==T & lat<=23.5 & lat>=-23.5)) 
dim(subset(NPP_all, is.na(Nmin)==T & lat<=50 & lat>23.5))
dim(subset(NPP_all, is.na(Nmin)==T & lat>= -50 & lat< -23.5))
dim(subset(NPP_all, is.na(Nmin)==T ))

#summarise number of sites
dim(subset(NPP_all,is.na(Nmin)==TRUE) %>% group_by(site)  %>% summarise(mean = mean(lon)))

@@

### Pre-process data
```{r}
#leaf Nmass
###2. leaf Nmass basing on a site-species model
SP_input <- read.csv(file="~/data/leaf_traits/combined_leaf_traits_updated.csv") #new one
summary(SP_input$C_percent)
dim(subset(SP_input,C_percent>0))
dim(unique(subset(SP_input,C_percent>0)[,c("lon","lat")]))
#median of value of leaf C = 0.47 or 47%

@@

### Fit model
```{r}
#Fit (Nmass) ~ Ns + Nr * (Vcmax25/LMA) - for site-species data
n1 <- lmer(nmass_a~vcmax25_lma_a + (1|sitename_a)+(1|species_a))
summary(n1)
r.squaredGLMM(n1)

@@

### Forest Root C:N 
```{r warning=FALSE}
# Root C/N = 94 - as derived from median values of collected samples
NPP_forest_sitemean <- aggregate(NPP_forest,by=list(NPP_forest$site), FUN=mean, na.rm=TRUE) 
summary(NPP_forest_sitemean$CN_root_final) # using median = 94
dim(subset(NPP_forest,CN_root_final>0))

@@

NRE_Dong_df$source <- "Dong"
NRE_Du_df$source <- "Du"
NRE_df <- rbind(NRE_Du_df,NRE_Dong_df)
summary(NRE_df$NRE)
length(NRE_df$NRE)
#median of NRE in grassland is 0.69, site  =26

#final model look
#bp_model,anpp_tnpp_model,anpp_leafnpp_model,bp_grass_model,0.49/0.51,n1,nre_model
```

@@

b1 <- as.ggplot(~barplot(vif_bp, main = "VIF of Forest BP model", horiz = TRUE, col = "steelblue",
                         names.arg = c("Tg", "fAPAR", "ln PPFD", "ln soil C/N", "ln age", "ln vpd")))
b2 <- as.ggplot(~barplot(vif_anpp_tnpp, main = "VIF of Forest ANPP/BP model", horiz = TRUE, col = "steelblue",
                         names.arg = c("Tg", "fAPAR", "ln PPFD", "ln soil C/N", "ln age", "ln vpd")))
b3 <- as.ggplot(~barplot(vif_anpp_leafnpp, main = "VIF of Forest leaf-NPP/ANPP model", horiz = TRUE, col = "steelblue",
                         names.arg = c("Tg", "fAPAR", "ln PPFD", "ln soil C/N", "ln age", "ln vpd")))
b4 <- as.ggplot(~barplot(vif_bp_grass, main = "VIF of Grassland BP model", horiz = TRUE, col = "steelblue",
                         names.arg = c("Tg", "ln PPFD", "ln vpd", "ln soil C/N", "fAPAR")))
plot_grid(b1,b2,b3,b4,
          labels = c('(a)','(b)','(c)','(d)'),
          ncol=2,label_x = 0.9,label_y=0.92)+white
ggsave(paste("./output/newphy_figs6.jpg",sep=""),width = 10, height = 13)
```

@@

p2 <- analyse_modobs2(NPP_forest,"pred_anpp", "ANPP_2",type = "points",relative=TRUE)$gg+ larger_size+coord_obs_pred()+
  labs(y = ~paste("Forest ", ANPP[obs.], " (gC m"^-2,"yr"^-1,")")) +labs(x = ~paste("Forest ", ANPP[pred.], " (gC m"^-2,"yr"^-1,")"))

p3 <- analyse_modobs2(NPP_forest,"pred_lnpp","NPP.foliage", type = "points",relative=TRUE)$gg + larger_size+coord_obs_pred()+
  labs(y = ~paste("Forest leaf ", NPP[obs.], " (gC m"^-2,"yr"^-1,")")) +labs(x = ~paste("Forest leaf ", NPP[pred.], " (gC m"^-2,"yr"^-1,")"))

p4 <- analyse_modobs2(NPP_forest, "pred_wnpp","NPP.wood",type = "points",relative=TRUE)$gg+ larger_size+coord_obs_pred()+
  labs(y = ~paste("Forest wood ", NPP[obs.], " (gC m"^-2,"yr"^-1,")")) +labs(x = ~paste("Forest wood ", NPP[pred.], " (gC m"^-2,"yr"^-1,")"))

p5 <- analyse_modobs2(NPP_forest,"pred_bnpp","BNPP_1", type = "points",relative=TRUE)$gg+ larger_size+coord_obs_pred()+
  labs(y = ~paste("Forest ", BNPP[obs.], " (gC m"^-2,"yr"^-1,")")) +labs(x = ~paste("Forest ", BNPP[pred.], " (gC m"^-2,"yr"^-1,")"))

@@

#check how many samples = 225, sites = 84
dim(subset(NPP_forest,is.na(pred_nuptake)==F & is.na(Nmin)==F))
dim(unique(subset(NPP_forest,pred_nuptake>0 & Nmin>0)[c("lon","lat")]))

@@

summary((lm(anpp_a~-1+tnpp_a,data=grassland_sitemean))) #0.49 as constant scalling

@@

p9 <- analyse_modobs2(NPP_grassland,"grassland_pred_anpp","ANPP_2", type = "points",relative=TRUE)$gg + larger_size+coord_obs_pred()+
  labs(y = ~paste("Grassland ", ANPP[obs.], " (gC m"^-2,"yr"^-1,")")) +labs(x = ~paste("Grassland ", ANPP[pred.], " (gC m"^-2,"yr"^-1,")"))

p10 <- analyse_modobs2(NPP_grassland,"grassland_pred_bnpp","BNPP_1", type = "points",relative=TRUE)$gg + larger_size+coord_obs_pred()+
  labs(y = ~paste("Grassland ", BNPP[obs.], " (gC m"^-2,"yr"^-1,")")) +labs(x = ~paste("Grassland ", BNPP[pred.], " (gC m"^-2,"yr"^-1,")"))

@@

```{r}
#fig.2 validation
plot_grid(p1,p2,p5,
          p8,p9,p10,
          p3,p4,p11,
          p6,p12,p7, 
          labels = c('(a)','(b)','(c)','(d)','(e)','(f)','(g)','(h)','(i)','(j)','(k)','(l)'),
          ncol=3,label_x = 0.9,label_y=0.92,label_size = 25)+white
ggsave(paste("./output/newphy_fig1.jpg",sep=""),width = 24, height = 25)

@@

a3 <- gg$ggmap +
  geom_point(data=npp_f1,aes(lon,lat),col="red",size=1.5)+
  geom_point(data=npp_g1,aes(lon,lat),col="blue",size=1.5)+
  labs(title = paste("BP:", total_value, "PgC/yr", sep=" " ))+
  theme_grey(base_size = 12)+ white

a4 <- gg$gglegend+labs(title = ~paste("gC m"^-2,"yr"^-1))+ white

@@

a5 <- gg$ggmap +
  geom_point(data=anpp_f1,aes(lon,lat),col="red",size=1.5)+
  geom_point(data=anpp_g1,aes(lon,lat),col="blue",size=1.5)+
  labs(title = paste("ANPP:", total_value, "PgC/yr", sep=" " ))+
  theme_grey(base_size = 12)+ white

a6 <- gg$gglegend+labs(title = ~paste("gC m"^-2,"yr"^-1))+ white

@@

total_value <- round(mean(leafcn_pft,na.rm=TRUE),2)
a7 <- gg$ggmap +
  geom_point(data=laefcn,aes(lon,lat),col="red",size=1.5)+
  labs(title = paste("Leaf C/N: ", total_value))+
  theme_grey(base_size = 12)+ white

a8 <- gg$gglegend+ white

@@

a9 <- gg$ggmap +
  geom_point(data=nre_site,aes(lon,lat),col="red",size=1.5)+
  labs(title = paste("NRE: ", total_value))+
  theme_grey(base_size = 12)+ white

a10 <- gg$gglegend+ white

@@

a11 <- gg$ggmap +
  geom_point(data=nuptake_f1,aes(lon,lat),col="red",size=1.5)+
  labs(title = paste("N uptake: ", total_value, "TgN/yr", sep=" " ))+
  theme_grey(base_size = 12)+ white

a12 <- gg$gglegend+labs(title = ~paste("gN m"^-2,"yr"^-1))+ white

@@

a13 <- gg$ggmap +
  labs(title = paste("NUE: ", total_value, " ", sep=" " ))+
  theme_grey(base_size = 12)+ white

a14 <- gg$gglegend+ white

@@

#this is for showing points
ggsave(paste("./output/newphy_figs5.jpg",sep=""),width = 16, height = 12)

@@

## Figure 3 without points
```{r}
#preparing one without showing points - in MS
total_value <- round(sum(all_maps[,"npp_pft"]*conversion,na.rm=TRUE),2)
gg <- plot_map3(na.omit(all_maps[,c("lon","lat","npp_pft")]),
                varnam = "npp_pft",latmin = -65, latmax = 85,combine=FALSE)
a3 <- gg$ggmap +
  labs(title = paste("BP:", total_value, "PgC/yr", sep=" " ))+
  theme_grey(base_size = 12)+ white
a4 <- gg$gglegend+labs(title = ~paste("gC m"^-2,"yr"^-1))+ white

#3.anpp
total_value <- round(sum(all_maps[,"anpp_pft"]*conversion,na.rm=TRUE),2)
gg <- plot_map3(na.omit(all_maps[,c("lon","lat","anpp_pft")]),
                varnam = "anpp_pft",latmin = -65, latmax = 85,combine=FALSE)
a5 <- gg$ggmap +
  labs(title = paste("ANPP:", total_value, "PgC/yr", sep=" " ))+
  theme_grey(base_size = 12)+ white
a6 <- gg$gglegend+labs(title = ~paste("gC m"^-2,"yr"^-1))+ white

@@

total_value <- round(mean(leafcn_pft,na.rm=TRUE),2)
a7 <- gg$ggmap +
  labs(title = paste("Leaf C/N: ", total_value))+
  theme_grey(base_size = 12)+ white
a8 <- gg$gglegend+ white

@@

a9 <- gg$ggmap +
  labs(title = paste("NRE: ", total_value))+
  theme_grey(base_size = 12)+ white
a10 <- gg$gglegend+ white

#6. nuptake
total_value <- 1000*round(sum(all_maps[,"nuptake_pft"]*conversion,na.rm=TRUE),2) #unit convert from PgN/yr to TgN/yr
gg <- plot_map3(na.omit(all_maps[,c("lon","lat","nuptake_pft")]),
                varnam = "nuptake_pft",latmin = -65, latmax = 85,combine=FALSE)
a11 <- gg$ggmap +
  labs(title = paste("N uptake: ", total_value, "TgN/yr", sep=" " ))+
  theme_grey(base_size = 12)+ white

a12 <- gg$gglegend+labs(title = ~paste("gN m"^-2,"yr"^-1))+ white

@@

a13 <- gg$ggmap +
  labs(title = paste("NUE: ", total_value, " ", sep=" " ))+
  theme_grey(base_size = 12)+ white

a14 <- gg$gglegend+ white

plot_grid(a3,a4,a5,a6,
          a7,a8,a9,a10,
          a11,a12,a13,a14,
          nrow=3,
          rel_widths = c(4.5/12, 1.5/12,4.5/12,1.5/12),
          labels = c('(a)',' ','(b)',' ',
                     '(c)',' ','(d)',' ',
                     '(e)',' ','(f)',' '))
ggsave(paste("./output/newphy_fig2.jpg",sep=""),width = 16, height = 12)

@@

nue_all$name <- factor(nue_all$name,levels = c("90°S ~ 60°S","60°S ~ 30°S","30°S ~ 0",
                                               "0 ~ 30°N","30°N ~ 60°N","60°N ~ 90°N"))
nue_all <- subset(nue_all,name!="90°S ~ 60°S")
a1 <- ggplot(data = nue_all) + stat_summary(mapping = aes(y = name, x = nue_CNrt),fun.min = function(z) { quantile(z,0.25) },fun.max = function(z) { quantile(z,0.75) },fun = median,color="blue")+ geom_vline(xintercept=0, linetype="dashed")+labs(y= " ", x = "Soil C/N effect") +larger_size
a2 <- ggplot(data = nue_all) + stat_summary(mapping = aes(y = name, x = nue_age),fun.min = function(z) { quantile(z,0.25) },fun.max = function(z) { quantile(z,0.75) },fun = median,color="blue")+ geom_vline(xintercept=0, linetype="dashed")+labs(y= " ", x = "Age effect") +larger_size
a3 <- ggplot(data = nue_all) + stat_summary(mapping = aes(y = name, x = nue_fAPAR),fun.min = function(z) { quantile(z,0.25) },fun.max = function(z) { quantile(z,0.75) },fun = median,color="blue")+ geom_vline(xintercept=0, linetype="dashed")+labs(y= " ", x = "fAPAR effect") +larger_size
a4 <- ggplot(data = nue_all) + stat_summary(mapping = aes(y = name, x = nue_Tg),fun.min = function(z) { quantile(z,0.25) },fun.max = function(z) { quantile(z,0.75) },fun = median,color="blue")+ geom_vline(xintercept=0, linetype="dashed")+labs(y= " ", x = "Tg effect") +larger_size
a5 <- ggplot(data = nue_all) + stat_summary(mapping = aes(y = name, x = nue_vpd),fun.min = function(z) { quantile(z,0.25) },fun.max = function(z) { quantile(z,0.75) },fun = median,color="blue")+ geom_vline(xintercept=0, linetype="dashed")+labs(y= " ", x = "D effect") +larger_size
a6 <- ggplot(data = nue_all) + stat_summary(mapping = aes(y = name, x = nue_PPFD),fun.min = function(z) { quantile(z,0.25) },fun.max = function(z) { quantile(z,0.75) },fun = median,color="blue")+ geom_vline(xintercept=0, linetype="dashed")+labs(y= " ", x = "PPFD effect") +larger_size
a7 <- ggplot(data = nue_all) + stat_summary(mapping = aes(y = name, x = nue_vcmax25),fun.min = function(z) { quantile(z,0.25) },fun.max = function(z) { quantile(z,0.75) },fun = median,color="blue")+ geom_vline(xintercept=0, linetype="dashed")+labs(y= " ", x = "Vcmax25 effect") +larger_size
a8 <- ggplot(data = nue_all) + stat_summary(mapping = aes(y = name, x = nue_LMA),fun.min = function(z) { quantile(z,0.25) },fun.max = function(z) { quantile(z,0.75) },fun = median,color="blue")+ geom_vline(xintercept=0, linetype="dashed")+labs(y= " ", x = "LMA effect") +larger_size
a9 <- ggplot(data = nue_all) + stat_summary(mapping = aes(y = name, x = NUE),fun.min = function(z) { quantile(z,0.25) },fun.max = function(z) { quantile(z,0.75) },fun = median,color="blue")+labs(y= " ", x = "NUE") +larger_size

>>>>

larger_size <- theme(axis.text=element_text(size=20),axis.title=element_text(size=20), plot.subtitle=element_text(size=15))
larger_plot_title<-theme(plot.title = element_text(size=15))
```

@@

(some metric info such as number of sites and species was shown as 'metric_info', that will be inputted in Method text)
(metric info was primarily using individual numbers in Fig.1 - validation figure)

@@

#metric_info check some percentage
dim(subset(NPP_all, is.na(Nmin)==T & pft =="Forest"))
dim(subset(NPP_all, is.na(Nmin)==T & pft =="Grassland"))

dim(subset(NPP_all, is.na(Nmin)==T & lat<=23.5 & lat>=-23.5)) 
dim(subset(NPP_all, is.na(Nmin)==T & lat<=50 & lat>23.5))
dim(subset(NPP_all, is.na(Nmin)==T & lat>= -50 & lat< -23.5))

dim(subset(NPP_all, is.na(Nmin)==T ))

#check measured data casues what extent of reduction
nrow(subset(NPP_all,is.na(Nmin)==T &is.na(observedfAPAR)==F&
           is.na(age)==F&is.na(soilCN)==F))
1-(133/977)
#summarise number of sites
dim(subset(NPP_all,is.na(Nmin)==TRUE) %>% group_by(site)  %>% summarise(mean = mean(lon)))

@@

### Pre-process data
```{r}
#leaf Nmass
###2. leaf Nmass basing on a site-species model
SP_input <- read.csv(file="~/data/leaf_traits/combined_leaf_traits_updated.csv") #new one
summary(SP_input$C_percent)
dim(subset(SP_input,C_percent>0))
dim(unique(subset(SP_input,C_percent>0)[,c("lon","lat")]))
#metric_info
#median of value of leaf C = 0.47 or 47%

@@

### Fit model
```{r}
#Fit (Nmass) ~ Ns + Nr * (Vcmax25/LMA) - for site-species data
#metric_info: site and species number of Nmass model
n1 <- lmer(nmass_a~vcmax25_lma_a + (1|sitename_a)+(1|species_a))
summary(n1)
r.squaredGLMM(n1)

@@

### Forest Root C:N 
```{r warning=FALSE}
#metric_info
# Root C/N = 94 - as derived from median values of collected samples
NPP_forest_sitemean <- aggregate(NPP_forest,by=list(NPP_forest$site), FUN=mean, na.rm=TRUE) 
summary(NPP_forest_sitemean$CN_root_final) # using median = 94
dim(subset(NPP_forest,CN_root_final>0))

@@

NRE_Dong_df$source <- "Dong"
NRE_Du_df$source <- "Du"
NRE_df <- rbind(NRE_Du_df,NRE_Dong_df)
summary(NRE_df$NRE)
length(NRE_df$NRE)
#median of NRE in grassland is 0.69, site  =26
#metric_info: site number of NRE in total: forest = 184 (shown in Fig.1), grassland  = 26 (shown here). Total = 210
#final model look
#bp_model,anpp_tnpp_model,anpp_leafnpp_model,bp_grass_model,0.49/0.51,n1,nre_model
```

@@

b1 <- as.ggplot(~barplot(vif_bp, main = "VIF of Forest BP model", horiz = TRUE, col = "steelblue",
                         names.arg = c("Tg", "fAPAR", "ln PPFD", "ln soil C:N", "ln age", "ln vpd")))
b2 <- as.ggplot(~barplot(vif_anpp_tnpp, main = "VIF of Forest ABP/BP model", horiz = TRUE, col = "steelblue",
                         names.arg = c("Tg", "fAPAR", "ln PPFD", "ln soil C:N", "ln age", "ln vpd")))
b3 <- as.ggplot(~barplot(vif_anpp_leafnpp, main = "VIF of Forest leaf-BP/ABP model", horiz = TRUE, col = "steelblue",
                         names.arg = c("Tg", "fAPAR", "ln PPFD", "ln soil C:N", "ln age", "ln vpd")))
b4 <- as.ggplot(~barplot(vif_bp_grass, main = "VIF of Grassland BP model", horiz = TRUE, col = "steelblue",
                         names.arg = c("Tg", "ln PPFD", "ln vpd", "ln soil C:N", "fAPAR")))
plot_grid(b1,b2,b3,b4,
          labels = c('(a)','(b)','(c)','(d)'),
          ncol=2,label_x = 0.9,label_y=0.92)+white
ggsave(paste("./output/figs4.jpg",sep=""),width = 10, height = 13)
```

@@

p2 <- analyse_modobs2(NPP_forest,"pred_anpp", "ANPP_2",type = "points",relative=TRUE)$gg+ larger_size+coord_obs_pred()+
  labs(y = ~paste("Forest ", ABP[obs.], " (gC m"^-2,"yr"^-1,")")) +labs(x = ~paste("Forest ", ABP[pred.], " (gC m"^-2,"yr"^-1,")"))

p3 <- analyse_modobs2(NPP_forest,"pred_lnpp","NPP.foliage", type = "points",relative=TRUE)$gg + larger_size+coord_obs_pred()+
  labs(y = ~paste("Forest leaf ", BP[obs.], " (gC m"^-2,"yr"^-1,")")) +labs(x = ~paste("Forest leaf ", BP[pred.], " (gC m"^-2,"yr"^-1,")"))

p4 <- analyse_modobs2(NPP_forest, "pred_wnpp","NPP.wood",type = "points",relative=TRUE)$gg+ larger_size+coord_obs_pred()+
  labs(y = ~paste("Forest wood ", BP[obs.], " (gC m"^-2,"yr"^-1,")")) +labs(x = ~paste("Forest wood ", BP[pred.], " (gC m"^-2,"yr"^-1,")"))

p5 <- analyse_modobs2(NPP_forest,"pred_bnpp","BNPP_1", type = "points",relative=TRUE)$gg+ larger_size+coord_obs_pred()+
  labs(y = ~paste("Forest ", BBP[obs.], " (gC m"^-2,"yr"^-1,")")) +labs(x = ~paste("Forest ", BBP[pred.], " (gC m"^-2,"yr"^-1,")"))

@@

#metric_info: site and individual numbers of N uptake
#check how many samples = 225, sites = 84
dim(subset(NPP_forest,is.na(pred_nuptake)==F & is.na(Nmin)==F))
dim(unique(subset(NPP_forest,pred_nuptake>0 & Nmin>0)[c("lon","lat")]))

@@

summary((lm(anpp_a~-1+tnpp_a,data=grassland_sitemean))) #0.50 as constant scalling

@@

p9 <- analyse_modobs2(NPP_grassland,"grassland_pred_anpp","ANPP_2", type = "points",relative=TRUE)$gg + larger_size+coord_obs_pred()+
  labs(y = ~paste("Grassland ", ABP[obs.], " (gC m"^-2,"yr"^-1,")")) +labs(x = ~paste("Grassland ", ABP[pred.], " (gC m"^-2,"yr"^-1,")"))

p10 <- analyse_modobs2(NPP_grassland,"grassland_pred_bnpp","BNPP_1", type = "points",relative=TRUE)$gg + larger_size+coord_obs_pred()+
  labs(y = ~paste("Grassland ", BBP[obs.], " (gC m"^-2,"yr"^-1,")")) +labs(x = ~paste("Grassland ", BBP[pred.], " (gC m"^-2,"yr"^-1,")"))

@@

```{r}
#fig.2 validation
plot_grid(p1,p2,p5,
          p8,p9,p10,
          p3,p4,p11,
          p6,p12,p7, 
          labels = c('(a)','(b)','(c)','(d)','(e)','(f)','(g)','(h)','(i)','(j)','(k)','(l)'),
          ncol=3,label_x = 0.9,label_y=0.92,label_size = 25)+white
ggsave(paste("./output/fig1.jpg",sep=""),width = 24, height = 25)

@@

a3 <- gg$ggmap +
  geom_point(data=npp_f1,aes(lon,lat),col="red",size=1.5)+
  geom_point(data=npp_g1,aes(lon,lat),col="blue",size=1.5)+
  labs(title = paste("BP:", total_value, "PgC/yr", sep=" " ))+
  theme_grey(base_size = 12)+ white+larger_plot_title

a4 <- gg$gglegend+labs(title = ~paste("gC m"^-2,"yr"^-1))+ white+larger_plot_title

@@

a5 <- gg$ggmap +
  geom_point(data=anpp_f1,aes(lon,lat),col="red",size=1.5)+
  geom_point(data=anpp_g1,aes(lon,lat),col="blue",size=1.5)+
  labs(title = paste("ABP:", total_value, "PgC/yr", sep=" " ))+
  theme_grey(base_size = 12)+ white+larger_plot_title

a6 <- gg$gglegend+labs(title = ~paste("gC m"^-2,"yr"^-1))+ white+larger_plot_title

@@

total_value <- round(mean(leafcn_pft,na.rm=TRUE),2)
a7 <- gg$ggmap +
  geom_point(data=laefcn,aes(lon,lat),col="red",size=1.5)+
  labs(title = paste("Leaf C:N: ", total_value))+
  theme_grey(base_size = 12)+ white+larger_plot_title

a8 <- gg$gglegend+ white+larger_plot_title

@@

a9 <- gg$ggmap +
  geom_point(data=nre_site,aes(lon,lat),col="red",size=1.5)+
  labs(title = paste("NRE: ", total_value))+
  theme_grey(base_size = 12)+ white+larger_plot_title

a10 <- gg$gglegend+ white+larger_plot_title

@@

a11 <- gg$ggmap +
  geom_point(data=nuptake_f1,aes(lon,lat),col="red",size=1.5)+
  labs(title = paste("N uptake: ", total_value, "TgN/yr", sep=" " ))+
  theme_grey(base_size = 12)+ white+larger_plot_title

a12 <- gg$gglegend+labs(title = ~paste("gN m"^-2,"yr"^-1))+ white+larger_plot_title

@@

a13 <- gg$ggmap +
  labs(title = paste("NUE: ", total_value, " ", sep=" " ))+
  theme_grey(base_size = 12)+ white+larger_plot_title

a14 <- gg$gglegend+ white+larger_plot_title

@@

#this is for showing points
ggsave(paste("./output/figs3.jpg",sep=""),width = 16, height = 12)

@@

## Figure 3 without points
```{r}
#preparing one without showing points - in MS
total_value <- round(sum(all_maps[,"npp_pft"]*conversion,na.rm=TRUE),2)
gg <- plot_map3(na.omit(all_maps[,c("lon","lat","npp_pft")]),
                varnam = "npp_pft",latmin = -65, latmax = 85,combine=FALSE)
a3 <- gg$ggmap +
  labs(title = paste("BP:", total_value, "PgC/yr", sep=" " ))+
  theme_grey(base_size = 12)+ white+larger_plot_title
a4 <- gg$gglegend+labs(title = ~paste("gC m"^-2,"yr"^-1))+ white+larger_plot_title

#3.anpp
total_value <- round(sum(all_maps[,"anpp_pft"]*conversion,na.rm=TRUE),2)
gg <- plot_map3(na.omit(all_maps[,c("lon","lat","anpp_pft")]),
                varnam = "anpp_pft",latmin = -65, latmax = 85,combine=FALSE)
a5 <- gg$ggmap +
  labs(title = paste("ABP:", total_value, "PgC/yr", sep=" " ))+
  theme_grey(base_size = 12)+ white+larger_plot_title
a6 <- gg$gglegend+labs(title = ~paste("gC m"^-2,"yr"^-1))+ white+larger_plot_title

@@

total_value <- round(mean(leafcn_pft,na.rm=TRUE),2)
a7 <- gg$ggmap +
  labs(title = paste("Leaf C:N: ", total_value))+
  theme_grey(base_size = 12)+ white+larger_plot_title
a8 <- gg$gglegend+ white+larger_plot_title

@@

a9 <- gg$ggmap +
  labs(title = paste("NRE: ", total_value))+
  theme_grey(base_size = 12)+ white+larger_plot_title
a10 <- gg$gglegend+ white+larger_plot_title

#6. nuptake
total_value <- 1000*round(sum(all_maps[,"nuptake_pft"]*conversion,na.rm=TRUE),2) #unit convert from PgN/yr to TgN/yr
gg <- plot_map3(na.omit(all_maps[,c("lon","lat","nuptake_pft")]),
                varnam = "nuptake_pft",latmin = -65, latmax = 85,combine=FALSE)
a11 <- gg$ggmap +
  labs(title = paste("N uptake: ", total_value, "TgN/yr", sep=" " ))+
  theme_grey(base_size = 12)+ white+larger_plot_title

a12 <- gg$gglegend+labs(title = ~paste("gN m"^-2,"yr"^-1))+ white+larger_plot_title

@@

a13 <- gg$ggmap +
  labs(title = paste("NUE: ", total_value, " ", sep=" " ))+
  theme_grey(base_size = 12)+ white+larger_plot_title

a14 <- gg$gglegend+ white+larger_plot_title

plot_grid(a3,a4,a5,a6,
          a7,a8,a9,a10,
          a11,a12,a13,a14,
          nrow=3,
          rel_widths = c(4.5/12, 1.5/12,4.5/12,1.5/12),
          labels = c('(a)',' ','(b)',' ',
                     '(c)',' ','(d)',' ',
                     '(e)',' ','(f)',' '))
ggsave(paste("./output/fig2.jpg",sep=""),width = 16, height = 12)

@@

nue_all$name <- factor(nue_all$name,levels = c("90°S ~ 60°S","60°S ~ 30°S","30°S ~ 0",
                                               "0 ~ 30°N","30°N ~ 60°N","60°N ~ 90°N"))
nue_all <- subset(nue_all,name!="90°S ~ 60°S")
a1 <- ggplot(data = nue_all) + stat_summary(mapping = aes(y = name, x = nue_CNrt),fun.min = function(z) { quantile(z,0.25) },fun.max = function(z) { quantile(z,0.75) },fun = median,color="blue")+ geom_vline(xintercept=0, linetype="dashed")+labs(y= " ", x = "Soil C:N effect") +larger_size
a2 <- ggplot(data = nue_all) + stat_summary(mapping = aes(y = name, x = nue_age),fun.min = function(z) { quantile(z,0.25) },fun.max = function(z) { quantile(z,0.75) },fun = median,color="blue")+ geom_vline(xintercept=0, linetype="dashed")+labs(y= " ", x = "Age effect") +larger_size
a3 <- ggplot(data = nue_all) + stat_summary(mapping = aes(y = name, x = nue_fAPAR),fun.min = function(z) { quantile(z,0.25) },fun.max = function(z) { quantile(z,0.75) },fun = median,color="blue")+ geom_vline(xintercept=0, linetype="dashed")+labs(y= " ", x = "fAPAR effect") +larger_size
a4 <- ggplot(data = nue_all) + stat_summary(mapping = aes(y = name, x = nue_Tg),fun.min = function(z) { quantile(z,0.25) },fun.max = function(z) { quantile(z,0.75) },fun = median,color="blue")+ geom_vline(xintercept=0, linetype="dashed")+labs(y= " ", x = "Tg effect") +larger_size
a5 <- ggplot(data = nue_all) + stat_summary(mapping = aes(y = name, x = nue_vpd),fun.min = function(z) { quantile(z,0.25) },fun.max = function(z) { quantile(z,0.75) },fun = median,color="blue")+ geom_vline(xintercept=0, linetype="dashed")+labs(y= " ", x = "D effect") +larger_size
a6 <- ggplot(data = nue_all) + stat_summary(mapping = aes(y = name, x = nue_PPFD),fun.min = function(z) { quantile(z,0.25) },fun.max = function(z) { quantile(z,0.75) },fun = median,color="blue")+ geom_vline(xintercept=0, linetype="dashed")+labs(y= " ", x = "PPFD effect") +larger_size
a7 <- ggplot(data = nue_all) + stat_summary(mapping = aes(y = name, x = nue_vcmax25),fun.min = function(z) { quantile(z,0.25) },fun.max = function(z) { quantile(z,0.75) },fun = median,color="blue")+ geom_vline(xintercept=0, linetype="dashed")+labs(y= " ", x = "Vcmax25 effect") +larger_size
a8 <- ggplot(data = nue_all) + stat_summary(mapping = aes(y = name, x = nue_LMA),fun.min = function(z) { quantile(z,0.25) },fun.max = function(z) { quantile(z,0.75) },fun = median,color="blue")+ geom_vline(xintercept=0, linetype="dashed")+labs(y= " ", x = "LMA effect") +larger_size
a9 <- ggplot(data = nue_all) + stat_summary(mapping = aes(y = name, x = NUE),fun.min = function(z) { quantile(z,0.25) },fun.max = function(z) { quantile(z,0.75) },fun = median,color="blue")+labs(y= " ", x = "NUE") +larger_size

aa1 <- ggplot(data = nue_all) + stat_summary(mapping = aes(y = name, x = CNrt),fun.min = function(z) { quantile(z,0.25) },fun.max = function(z) { quantile(z,0.75) },fun = median,color="black")+labs(y= " ", x = "Soil C:N") +larger_size
aa2 <- ggplot(data = nue_all) + stat_summary(mapping = aes(y = name, x = age),fun.min = function(z) { quantile(z,0.25) },fun.max = function(z) { quantile(z,0.75) },fun = median,color="black")+labs(y= " ", x = "Age") +larger_size
aa3 <- ggplot(data = nue_all) + stat_summary(mapping = aes(y = name, x = fAPAR),fun.min = function(z) { quantile(z,0.25) },fun.max = function(z) { quantile(z,0.75) },fun = median,color="black")+labs(y= " ", x = "fAPAR") +larger_size
aa4 <- ggplot(data = nue_all) + stat_summary(mapping = aes(y = name, x = Tg),fun.min = function(z) { quantile(z,0.25) },fun.max = function(z) { quantile(z,0.75) },fun = median,color="black")+labs(y= " ", x = "Tg") +larger_size
aa5 <- ggplot(data = nue_all) + stat_summary(mapping = aes(y = name, x = vpd),fun.min = function(z) { quantile(z,0.25) },fun.max = function(z) { quantile(z,0.75) },fun = median,color="black")+labs(y= " ", x = "D") +larger_size
aa6 <- ggplot(data = nue_all) + stat_summary(mapping = aes(y = name, x = PPFD),fun.min = function(z) { quantile(z,0.25) },fun.max = function(z) { quantile(z,0.75) },fun = median,color="black")+labs(y= " ", x = "PPFD")+larger_size 
aa7 <- ggplot(data = nue_all) + stat_summary(mapping = aes(y = name, x = vcmax25),fun.min = function(z) { quantile(z,0.25) },fun.max = function(z) { quantile(z,0.75) },fun = median,color="black")+labs(y= " ", x = "Vcmax25") +larger_size
aa8 <- ggplot(data = nue_all) + stat_summary(mapping = aes(y = name, x = LMA),fun.min = function(z) { quantile(z,0.25) },fun.max = function(z) { quantile(z,0.75) },fun = median,color="black")+labs(y= " ", x = "LMA") +larger_size

plot_grid(a1,a2,a3,a4,a5,a6,a7,a8,a9,
          labels = c('(a)','(b)','(c)','(d)','(e)','(f)','(g)','(h)','(i)'),label_size = 15)+white
ggsave(paste("./output/fig3.jpg",sep=""),width = 22, height = 10)

plot_grid(aa1,aa2,aa3,aa4,aa5,aa6,aa7,aa8,
          labels = c('(a)','(b)','(c)','(d)','(e)','(f)','(g)','(h)','(i)'),label_size = 15)+white
ggsave(paste("./output/figs7.jpg",sep=""),width = 22, height = 10)
```
